SDR enhancement by clouds

### 2024-03-14 GHI_enh_06_sza.tex
Commit 2024-03-14 12:14

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-40} \end{center}

@@

\begin{verbatim}
2024-03-14 09:10:56.9 athan@tyler GHI_enh_06_sza.R 0.671435 mins
\end{verbatim}

>>>>

\begin{verbatim}
Not changed:  ./GHI_enh_06_sza.R 
Not changed:  ./GHI_enh_00_variables.R 
Not changed:  ./GHI_enh_03_process.R 
Not changed:  ./data/GHI_enh_03_process.Rda 
\end{verbatim}

\begin{verbatim}
[1] FALSE
\end{verbatim}

\begin{verbatim}
Written `R_make_` file: .//.R_make.mk 
\end{verbatim}

@@

\hypertarget{sza-heatmaps-of-doy-and-sza}{%
\subsubsection{SZA heatmaps of DOY and SZA}\label{sza-heatmaps-of-doy-and-sza}}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}

@@

\begin{verbatim}
2024-03-14 09:41:49.6 athan@tyler GHI_enh_06_sza.R 0.259163 mins
\end{verbatim}

### 2024-03-14 article/article.Rmd
Commit 2024-03-14 12:14

<!-- Define CE and ECE -->
In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level exceeds the expected value under
sky, unobscured by clouds.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.

@@

We decided to use the Libradtran [@Emde2016] radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the AERONET monitoring network [@Giles2019; @Buis1998].  Our site
participates in AERONET, where we operate a Cimel photometer, colocated to
the CM-21 pyranometer, since 2003

>>>>

<!-- Define CE and ECE -->
In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies form instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@

We decided to use the Libradtran [@Emde2016] radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
participates in AERONET, where we operate a Cimel photometer, colocated to
the CM-21 pyranometer, since 2003
